---
title: "Synthetic Controls for VAR-Models - first implementation"
output:
  html_document:
    toc: yes
    toc_float: yes
    code_folding: show
    code_download: yes
---

-   Idea: Can obtain more accurate predictions and forecasts employing a time series approach

-   Implementation: Simple Autoregressive distributed lag model ($ARDL(p,q)$) of the form\
    $$Y_{t} = \mu_{0} +  \sum_{i = 1}^{k} \beta_{0,i}X_{t,i} + \beta_{1,i}X_{t-1,i} + … + \beta_{p,i}X_{t-p,i} + \gamma_{1} Y_{t-1} + … + \gamma_{q} Y_{t-q} + \epsilon_{t}$$

-   Use data from Basque-terrorism example by Abadie and Garadeazabal (2003), train $ARDL(p,q)$ and $SC$-model up to treatment occurrence in 1975 and compare results

# Synthetic control figures

-   Abadie and Garadeazabal use time-means in the 1960's as covariates

-   Many missing values before

-   Obtain nice $SC$-like looking plots

```{r setup, echo= TRUE, message = FALSE, warning = FALSE, results='hide'}
library(dynamac)
library(forecast)
library(tidyverse)
library(tseries)
library(urca)
library(TSstudio)
library(dLagM)
library(Synth)
library(knitr)

data("basque")

dataprep.out <- dataprep(
  foo = basque,
  predictors = c("school.illit", "school.prim", "school.med",
                 "school.high", "school.post.high", "invest"),
  predictors.op = "mean",
  time.predictors.prior = 1964:1969,
  special.predictors = list(
    list("gdpcap", 1960:1969 ,"mean"),
    list("sec.agriculture", seq(1961, 1969, 2), "mean"),
    list("sec.energy", seq(1961, 1969, 2), "mean"),
    list("sec.industry", seq(1961, 1969, 2), "mean"),
    list("sec.construction", seq(1961, 1969, 2), "mean"),
    list("sec.services.venta", seq(1961, 1969, 2), "mean"),
    list("sec.services.nonventa", seq(1961, 1969, 2), "mean"),
    list("popdens",               1969,               "mean")),
  dependent = "gdpcap",
  unit.variable = "regionno",
  unit.names.variable = "regionname",
  time.variable = "year",
  treatment.identifier = 17,
  controls.identifier = c(2:16, 18),
  time.optimize.ssr = 1960:1969,
  time.plot = 1955:1997)

synth.out <- synth(data.prep.obj = dataprep.out, method = "BFGS")

df_out = data.frame(
  year = as.numeric(rownames(dataprep.out$Y1plot))) %>% 
  mutate(Basque = as.numeric(dataprep.out$Y1plot),
         SC_Basque = as.numeric(dataprep.out$Y0plot %*% synth.out$solution.w)) 

df_plot = df_out %>% 
  select(year, Basque) %>% 
  rename(value = Basque) %>% 
  mutate(type = "Basque") %>% 
  bind_rows(select(df_out, year, SC_Basque) %>% 
              rename(value = SC_Basque) %>% 
              mutate(type = "SC_Basque"))

ggplot(df_plot) +
  ggtitle("SC plot") + 
  aes(x = year, y = value, colour = type) +
  geom_line(size = 0.75) +
  scale_color_hue(direction = 1) +
  geom_vline(xintercept = 1975, linetype="dashed", size=.5)+
  ylim(0,12)+
  theme_minimal()

rm(dataprep.out, synth.out)
```

# ARDL comparison model

-   For sake of simplicity: Include only Cataluna and Madrid as donors (the only regions with positive weight in $SC$-model)

-   Use current and past GDP of the donors and past GDP of Basque country itself to estimate current GDP level in the Basque country

-   Train model until 1975, predict real GDP from 1956 ($t-1$) until 1975. Forecast GDP from 1976 onward

-   No deeper time series analysis (unit root testing, optimal $p,q$-values, etc.) at this point

```{r, echo=TRUE, message = FALSE, warning = FALSE}

df_help = basque %>% 
  filter(regionname %in% c("Basque Country (Pais Vasco)", "Cataluna", "Madrid (Comunidad De)"),
         year <= 1975)  %>% 
  select(year, regionname, gdpcap)

df = df_help %>% 
  filter(regionname == "Basque Country (Pais Vasco)") %>% 
  select(year, gdpcap) %>% 
  rename(gdpcap_Basque = gdpcap) %>% 
  bind_cols(df_help %>% 
              filter(regionname == "Cataluna") %>% 
              select(gdpcap) %>% 
              rename(gdpcap_Cataluna = gdpcap)) %>% 
  bind_cols(df_help %>% 
              filter(regionname == "Madrid (Comunidad De)") %>% 
              select(gdpcap) %>% 
              rename(gdpcap_Madrid = gdpcap)) 


model1 = dLagM::ardlDlm(formula = gdpcap_Basque ~ gdpcap_Cataluna + gdpcap_Madrid, data = df, p = 1, q = 1)
```

## Model output

```{r, echo=TRUE, message = FALSE, warning = FALSE}
# model output
summary(model1)
```

## Visualization

```{r, echo=TRUE, message = FALSE, warning = FALSE}
df = df %>% 
  bind_cols(as.data.frame(c(NA, (model1$model$fitted.values)))) %>% 
  rename(fitted = c(5)) %>% 
  filter(!is.na(fitted))

df_help = basque %>% 
  filter(regionname %in% c("Basque Country (Pais Vasco)", "Cataluna", "Madrid (Comunidad De)"),
         year > 1975)  %>% 
  select(year, regionname, gdpcap)

x = df_help %>% 
  filter(regionname == "Cataluna") %>% 
  select(gdpcap) %>% 
  rename(gdpcap_Cataluna = gdpcap) %>% 
  bind_cols(df_help %>% 
              filter(regionname == "Madrid (Comunidad De)") %>% 
              select(gdpcap) %>% 
              rename(gdpcap_Madrid = gdpcap)) %>% 
  t() %>% 
  as.matrix()

colnames(x) = paste0("V", c(1:22))

fc = forecast(model1, x, h = 22)

df_help = data.frame(
  year = c(1956:1997)) %>% 
  left_join(select(df, year, fitted), by = "year") %>% 
  mutate(forecast = (c(rep(NA, times = 20), fc$forecasts))) %>% 
  mutate(combined = ifelse(is.na(forecast), fitted, forecast))
  
df_plot  = df_plot %>% 
  bind_rows(select(df_help, year, combined) %>% 
              rename(value = combined) %>% 
              mutate(type = "ARDL_Basque")) 

ggplot(df_plot) +
  ggtitle("SC + ARDL plot") + 
  aes(x = year, y = value, colour = type) +
  geom_line(size = 0.75) +
  scale_color_hue(direction = 1) +
  geom_vline(xintercept = 1975, linetype="dashed", size=.5)+
  theme_minimal()
```

## RMSE

```{r, echo=TRUE, message = FALSE, warning = FALSE}
df_out = df_out %>% 
  left_join(select(df_help, year, combined), by = "year") %>% 
  rename(ARDL_Basque = combined)

# RMSE for SC

sqrt(mean((df_out$Basque[df_out$year <= 1975] - df_out$SC_Basque[df_out$year <= 1975])^2))

# RMSE for ARDL
sqrt(mean((df_out$Basque[df_out$year <= 1975] - df_out$ARDL_Basque[df_out$year <= 1975])^2, na.rm = T))
```

# Result

-    $ARDL$-model outperforms $SC$-model in terms of pre-treatment RMSE even though besides GDP, no additional covariates are included

-   Should pay careful attention to over-fitting-issues when using the $ARDL$-model
