\documentclass[11pt]{article}
\usepackage[a4paper, portrait, margin=1.1811in]{geometry}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
%\usepackage{helvet}
%\renewcommand{\familydefault}{\sfdefault}
\usepackage{etoolbox}
\usepackage{graphicx}
\usepackage{titlesec}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{xcolor} 
\usepackage{breakcites}
\usepackage{caption}
\usepackage{float}
\captionsetup[figure]{name=Figure}
\usepackage{setspace}
\graphicspath{ {./images/} }
\usepackage{scrextend}
\usepackage{subfigure}
\usepackage{tabularx}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{acronym}
\usepackage{comment}

% Math packs
\usepackage{amsmath}
\usepackage{amssymb}

% footnotes
\usepackage[hang, flushmargin]{footmisc}
\usepackage[colorlinks=true, citecolor=cyan]{hyperref}
\usepackage{footnotebackref}

\newcounter{lemma}
\newtheorem{lemma}{Lemma}
\newcounter{theorem}
\newtheorem{theorem}{Theorem}

%\pagestyle{plain}
\makeatletter
\patchcmd{\@maketitle}{\LARGE \@title}{\fontsize{16}{19.2}\selectfont\@title}{}{}
\makeatother

\usepackage{authblk}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\renewcommand\Authfont{\fontsize{12}{10.8}\selectfont}
\renewcommand\Affilfont{\fontsize{12}{10.8}\selectfont}
\renewcommand*{\Authsep}{, }
\renewcommand*{\Authand}{, }
\renewcommand*{\Authands}{, }
\newcommand{\rvec}{\mathrm {\mathbf {r}}} 
\renewcommand{\thetable}{S\arabic{table}}
\setlength{\affilsep}{2em}  
\newsavebox\affbox
\author[a]{\textbf{Jörg Breitung}}
\author[b]{\textbf{Lennart Bolwin}}
\author[b]{\textbf{Justus Töns}}
\affil[a]{University of Cologne, Chair of Statistics and Econometrics}
\affil[b]{University of Cologne, Chair of Statistics and Econometrics \newline
	Supervised by Prof. Dr. Jörg Breitung
}


\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsection{12pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsubsection{12pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}


\titleformat{\section}{\normalfont\fontsize{14}{15}\bfseries}{\thesection.}{1em}{}
\titleformat{\subsection}{\normalfont\fontsize{12}{15}\bfseries}{\thesubsection.}{1em}{}
\titleformat{\subsubsection}{\normalfont\fontsize{12}{15}\bfseries}{\thesubsubsection.}{1em}{}

\titleformat{\author}{\normalfont\fontsize{10}{15}\bfseries}{\thesection}{1em}{}

\title{\textbf{\huge Combining Synthetic Controls and VARs:}\\
	On the Estimation of Causal Effects in Time Series Data}
\date{}    

\begin{document}
	\onehalfspacing
	\pagestyle{headings}	
	\newpage
	\setcounter{page}{1}
	\renewcommand{\thepage}{\arabic{page}}
	
	
	
	\captionsetup[figure]{labelfont={bf},labelformat={default},labelsep=period,name={Figure }}	\captionsetup[table]{labelfont={bf},labelformat={default},labelsep=period,name={Table }}
	\setlength{\parskip}{0.5em}
	
	\maketitle
	
	\noindent\rule{15cm}{0.5pt}
	\begin{abstract}
		We argue that applications of \ac{SC} are faced with a self-selection problem. That is, the method is primarily applied to non-complex data structures that are straightforward to forecast, given the availability of donors in the post-treatment period. Using simulation  studies, we show that the high interpretability of \ac{SC} comes at the cost of poor predictions and forecasts, which are especially pronounced if the data generating process contains a time series structure. To address this issue, we introduce the intricacy-statistics that informs the applied researcher whether or not the data at hand exceeds a level of time series structure that \ac{SC} can handle. If the case, more flexible methodologies that combine the strengths of \ac{SC} and conventional time series techniques promise more accurate predictions and forecasts. Hence we introduce the new \ac{VARSC} estimator, that takes in account both the time series structure and the availability of donors. In order to implement these ideas, we introduce the R-package varsc that provides ready-to-use functions to compute the intricacy-statistics and, based on the magnitude of the statistics, the functionalities to estimate either the \ac{SC} or the \ac{VARSC} model. To probe the performance of our methodology outside the experimental setting, we apply it to three existing applications of \ac{SC}: Specifically, we show that our proposed model performs equally well like the SC-method. The result is striking because in contrast to the \ac{SC}-model, our models gets along without the informational contend of potential covariates. \\ \\
		
		\textbf{\textit{Keywords}}: \textit{Synthetic Control; Causality; VAR}
	\end{abstract}
	\noindent\rule{15cm}{0.4pt}
	
	
	% einzelne Abschnitte
	\newpage
	\doublespacing
	\input{0_acronyms}
	\newpage
	\tableofcontents
	\newpage
	\listoffigures
	\newpage
	\input{1_introduction}
	\newpage	
	\input{2_literature}
	\newpage
	\input{3_theory}
	\newpage	
	\input{4_simulation}
	\newpage
	\input{4_simulation_JT}
	\newpage
	\input{5_applications}
	\newpage
	\input{6_conclusion}
	
	\newpage
	\bibliographystyle{apalike} 
	\bibliography{mybib}
	
	\newpage
	\input{7_appendix}
	
\end{document}